---
title: "Research"
---

<!--html_preserve-->
<style type="text/css">
ul.CV {
list-style-type: none;
}
</style>
<!--/html_preserve-->

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(RefManageR)
```

I am currently a Senior Research Fellow at the School of Educational Sciences in Tallinn University (Estonia), and member of the Center of Excellence in Educational Innovation at the same university. A telecom engineer by training, I later pursued a Ph.D. and an academic career in the fields of technology-enhaced learning (TEL), computer-supported collaborative learning (CSCL), learning design (LD) and learning analytics (LA).

My research interests have always emphasized the **naturalistic observation of teaching and learning practice** using of a variety of methods, from unstructured qualitative observation and analysis, wearable sensors such as mobile eye-trackers. I have applied this variety of methods, for example, to understand teachers' classroom orchestration -- in what has been termed 'multimodal teaching analytics'. I have also proposed and evaluated **technologies to support educational practice**, from learning design tools to help teachers implement their pedagogical designs, to reflection tools that enable practitioners to gather and visualize data about their daily practice. Recently, I am joining these two research strands (naturalistic observation and support of professional practice), along with new data collection and analysis tools (e.g., diaries and epistemic network analysis) to investigate the field of **doctoral education**, of which I am an avid practitioner and educator (e.g., through doctoral workshops and my blog, [A Happy PhD](https://www.ahappyphd.org).

I have held  positions in well-known labs in technology-enhanced learning in Spain, Switzerland and Estonia, including a prestigious Marie Curie Fellowship. Throughout my research career, I have always worked in **multi-disciplinary** teams involving educational scientists, psychologists, and computer scientists. Learning from these inter-disciplinary contacts, I have used (and devised) a variety of theoretical frameworks and analytical lenses, both qualitative *and* quantitative.



# Academic Roles

* 2016 - 20
    + Senior Research Fellow - Center of Excellence in Educational Innovation, School of Educational Sciences, [Tallinn University](http://tlu.ee), Estonia.
* 2014 - 16
    + Scientist (Marie Curie Fellow) - [CHILI Lab](http://chili.epfl.ch/), [École Polytechnique Fédérale de Lausanne (EPFL)](http://epfl.ch/), Switzerland.
* 2012 - 13
    + Post-doctoral researcher - [GSIC-EMIC group](http://gsic.uva.es), [University of Valladolid](http://www.uva.es), Spain.
* 2009 - 2012
    + Doctoral researcher - [GSIC-EMIC group](http://gsic.uva.es), [University of Valladolid](http://www.uva.es), Spain.

*************

# Other Work & Research Experience

* Visiting Researcher - [Laboratoire d'Informatique de Grenoble](https://www.liglab.fr/), France (2013).
* International Fellow - [Center for Technology in Learning](https://www.sri.com/about/organization/education/ctl), SRI International, USA (2010). 
* Research & Development Engineer - [Telefónica I+D](http://tid.es/), Spain (2001-2008).
* Research & Development Intern - [Telefónica I+D](http://tid.es/), Spain (2000-2001).


*************

# Awards and Distinctions

* 2020
    + Estonian National Research Award (Social Sciences, Team Award), Estonian Academy of Sciences
* 2016
    + Best Paper Award, European Conference on Technology-Enhanced Learning.
* 2014 - 15
    + Marie Curie Intra-European Fellowship, European Commission.
* 2013
    + Best Doctoral Thesis Award, eMadrid (R&D Network on Educational Technology
in the Region of Madrid).
* 2012
    + Ph.D. Extraordinary Award, Engineering/Architecture Area, University of
Valladolid.



*************

# Education

* 2008 - 2012
    + PhD in Information and Communication Technologies - University of Valladolid, Spain.
* 1996 - 2001
    + BSc in Telecommunications Engineering.

*************

# Publications

(see [my Google Scholar profile](https://scholar.google.com/citations?user=ySpnj0MAAAAJ&hl=en&oi=ao) for a more up-to-date version with citation counts)


```{r echo=FALSE, results="asis",comment=FALSE, warning=F}
file_pubs <- ReadBib("cvreferences.bib", check=F,  .Encoding = "UTF-8")
dates <- unlist(unique(file_pubs$year))[order(unlist(unique(file_pubs$year)),decreasing = TRUE)]
#Prints references
for (date in dates) {
  cat(paste0("## ",date),"\n\n")
  print(file_pubs[list(year=date)],.opts = list(check.entries=F, style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n\n")
}

```
