---
title: "Research"
---

<!--html_preserve-->
<style type="text/css">
ul.CV {
list-style-type: none;
}
</style>
<!--/html_preserve-->

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(RefManageR)
```

My research interests lie at the intersection of **education and technology**, with a dash of human-computer interaction. I am mainly interested in understanding what happens in the (physical) classroom, and in blended learning settings that combine face-to-face and online activities. With that understanding, my aim is to support teachers and learners with novel technologies that support them in their **everyday** learning. I've paid special attention to more complex, active methods of learning such as collaborative learning, or the provision of timely feedback through learning analytics. In order to do that, I have used a variety of technologies and methods, from very simple [questionnaires aimed at reflection](http://prolearning.realto.ch), to [community-oriented platforms to support learning design by teachers](http://ilde.upf.edu), [augmented paper tabletops](http://chili.epfl.ch/page-110567-en.html), or cutting-edge [mobile eye-tracking technology](http://chili.epfl.ch/page-118328-en.html).



# Academic Roles

* 2016 - 19
    + Senior Research Fellow - Center of Excellence in Educational Innovation, School of Educational Sciences, [Tallinn University](http://tlu.ee), Estonia.
* 2014 - 16
    + Scientist (Marie Curie Fellow) - [CHILI Lab](http://chili.epfl.ch/), [École Polytechnique Fédérale de Lausanne (EPFL)](http://epfl.ch/), Switzerland.
* 2012 - 13
    + Post-doctoral researcher - [GSIC-EMIC group](http://gsic.uva.es), [University of Valladolid](http://www.uva.es), Spain.
* 2009 - 2012
    + Doctoral researcher - [GSIC-EMIC group](http://gsic.uva.es), [University of Valladolid](http://www.uva.es), Spain.

*************

# Other Work & Research Experience

* Visiting Researcher - [Laboratoire d'Informatique de Grenoble](https://www.liglab.fr/), France (2013).
* International Fellow - [Center for Technology in Learning](https://www.sri.com/about/organization/education/ctl), SRI International, USA (2010). 
* Research & Development Engineer - [Telefónica I+D](http://tid.es/), Spain (2001-2008).
* Research & Development Intern - [Telefónica I+D](http://tid.es/), Spain (2000-2001).


*************

# Awards and Distinctions

* 2016
    + Best Paper Award, European Conference on Technology-Enhanced Learning.
* 2014 - 15
    + Marie Curie Intra-European Fellowship, European Commission.
* 2013
    + Best Doctoral Thesis Award, eMadrid (R&D Network on Educational Technology
in the Region of Madrid).
* 2012
    + Ph.D. Extraordinary Award, Engineering/Architecture Area, University of
Valladolid.



*************

# Education

* 2008 - 2012
    + PhD in Information and Communication Technologies - University of Valladolid, Spain.
* 1996 - 2001
    + BSc in Telecommunications Engineering.

*************

# Publications


```{r echo=FALSE, results="asis",comment=FALSE, warning=F}
file_pubs <- ReadBib("cvreferences.bib", check=F)
dates <- unlist(unique(file_pubs$year))[order(unlist(unique(file_pubs$year)),decreasing = TRUE)]
#Prints recerences
for (date in dates) {
  cat(paste0("##",date),"\n")
  print(file_pubs[list(year=date)],.opts = list(check.entries=F, style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}

```
